Exploring and Predicting House Price in Nanjing: Geographically Imbalanced Distribution Across Districts and the Crucial Role of Unit Price and Bedroom Count in Predictioin

### 2023-12-08 output/paper/paper.qmd
Update figure captions and part of references

We used `Python` [@citePython] to obtain the datasets and `R` [@citeR] to do the analysis in this paper. We used pakage `requests` [@citeRequests], `parsel` [@citeParsel], and `csv` [@citeCsv] in `Python` to scrape the data, and then in `R`, we used packages `tidyverse` [@citeTidyverse], `stringr` [@citeStringr], and `here` [@citeHere] to clean and load the data as well as create figures. We used package `latex2expand` [@citeLatex2expand] to add labels to figures, `knitr` [@citeKnitr], `broom` [@citeBroom], and `gt` [@citeGt] to generate tables, and `corrplot` [@citeCorrplot] to make the correlation plot. We also used package `randomForest` [@citeRandomforest] and `Metrics` [@citeMetrics] to build up a Random Forest model and compare the results with Multiple Linear Regression model using different metrics. The color style of the figures was created referring to a R colors cheet-sheet [@citeRcolor].

@@

```{r}
#| label: tbl-data
#| tbl-cap: Description for variables
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: tbl-price
#| tbl-cap: Descriptive statistics about house price in each districts
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-con
#| fig-cap: Distribution of Area, Total Price, and Unit Price
#| echo: false
#| message: false
#| warning: false

@@

df_con |> ggplot(aes(x = value)) +
  geom_histogram(fill = "#A8D8B9") +
  facet_wrap(~key, scales = "free") +
  labs(y = "Number of house", x = "Variable value") +
  theme_minimal() +
  theme(axis.text = element_text(size = 7))

@@

```{r}
#| label: fig-dis
#| fig-cap: Number of house with different bedroom numbers, living room numbers, total floors, and detailed floor
#| echo: false
#| message: false
#| warning: false

@@

df_dis |> ggplot(aes(x = value)) +
  geom_bar(fill = "#A8D8B9") +
  facet_wrap(~key, scales = "free") +
  labs(y = "Number of House", x = "Variable value") +
  theme_minimal() +
  theme(axis.text = element_text(size = 7))
```

@@

```{r}
#| label: fig-char
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Proportion of house with difference decoration status and whether facing south in 11 districts
#| fig-subcap: 
#|   - "South-facing"
#|   - "Decoration"
#| layout-ncol: 2

data |> group_by(District, Facing_South) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Facing_South))) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(y = "Number of house", fill = "Whether south-facing") +
  scale_fill_manual(values = c("#A8D8B9", "#FFD966"), labels = c("No", "Yes")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 8))

data |> group_by(District, Furnished) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Furnished))) +
  geom_bar(stat = "identity") +
  labs(y = "Number of house", fill = "Decoration status") +
  theme_minimal() +
  scale_fill_manual(values = c("#7FCCE5", "#FF9A8B", "#A8D8B9", "#FFD966")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 8))
```

@@

```{r}
#| label: fig-area
#| fig-cap: Relationship between total house price and floor area for 11 districts and Nanjing city in total
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-price
#| fig-cap: Relationship between total house price and unit price for 11 districts and Nanjing city in total
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: tbl-model
#| tbl-cap: Summary of the multiple linear regression model
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-model
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Variable importance of the random forest model based on MSE and Node Purity
#| fig-subcap: 
#|   - "MSE"
#|   - "Node Purity"
#| layout-ncol: 2

@@

:Expression for MAE, RMSE, and $R^2$ {#tbl-expression}

@@

```{r}
#| label: tbl-metrics
#| tbl-cap: Summary of different metrics for test and train data for two models
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-cor
#| fig-cap: Correlation between each numeric variables
#| echo: false
#| warning: false
#| message: false

>>>>

We used `Python` [@citePython] to obtain the datasets and `R` [@citeR] to do the analysis in this paper. We used pakage `requests` [@citeRequests], `parsel` [@citeParsel], and `csv` [@citeCsv] in `Python` to scrape the data, and then in `R`, we used packages `tidyverse` [@citeTidyverse], `stringr` [@citeStringr], and `here` [@citeHere] to clean and load the data as well as create figures. We used package `latex2exp` [@citeLatex2exp] to add labels to figures, `knitr` [@citeKnitr], `broom` [@citeBroom], and `gt` [@citeGt] to generate tables, and `corrplot` [@citeCorrplot] to make the correlation plot. We also used package `randomForest` [@citeRandomforest] and `Metrics` [@citeMetrics] to build up a Random Forest model and compare the results with Multiple Linear Regression model using different metrics. The color style of the figures was created referring to a R colors cheet-sheet [@citeRcolor].

@@

```{r}
#| label: tbl-data
#| tbl-cap: Description for variables in the house price dataset for Nanjing
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: tbl-price
#| tbl-cap: Descriptive statistics about average house price, unit price, and floor area in each district
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-con
#| fig-cap: Distribution of floor area, house price, and unit price in Nanjing
#| echo: false
#| message: false
#| warning: false

@@

df_con |> ggplot(aes(x = value)) +
  geom_histogram(fill = "#A8D8B9") +
  facet_wrap(~key, scales = "free") +
  labs(y = "Number of houses", x = "Variable value") +
  theme_minimal() +
  theme(axis.text = element_text(size = 7))

@@

```{r}
#| label: fig-dis
#| fig-cap: Number of houses with different bedroom numbers, living room numbers, total floors, and detailed floor in Nanjing
#| echo: false
#| message: false
#| warning: false

@@

df_dis |> ggplot(aes(x = value)) +
  geom_bar(fill = "#A8D8B9") +
  facet_wrap(~key, scales = "free") +
  labs(y = "Number of houses", x = "Variable value") +
  theme_minimal() +
  theme(axis.text = element_text(size = 7))
```

@@

```{r}
#| label: fig-char
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Proportion of houses with different decoration status and orientations in 11 districts
#| fig-subcap: 
#|   - "South-facing"
#|   - "Decoration"
#| layout-ncol: 2

data |> group_by(District, Facing_South) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Facing_South))) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(y = "Number of houses", fill = "Whether south-facing") +
  scale_fill_manual(values = c("#A8D8B9", "#FFD966"), labels = c("No", "Yes")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 8))

data |> group_by(District, Furnished) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Furnished))) +
  geom_bar(stat = "identity") +
  labs(y = "Number of houses", fill = "Decoration status") +
  theme_minimal() +
  scale_fill_manual(values = c("#7FCCE5", "#FF9A8B", "#A8D8B9", "#FFD966")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 8))
```

@@

```{r}
#| label: fig-area
#| fig-cap: Relationship between house price and floor area for 11 districts and Nanjing city in total
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-price
#| fig-cap: Relationship between total price and unit price for 11 districts and Nanjing city in total
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: tbl-model
#| tbl-cap: Summary of the coefficient estimates for Multiple Linear Regression model
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-model
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Variable importance of the Random Forest model based on MSE and Node Purity
#| fig-subcap: 
#|   - "MSE"
#|   - "Node Purity"
#| layout-ncol: 2

@@

:Mathematical expression for 3 evaluation metrics: MAE, RMSE, and $R^2$ {#tbl-expression}

@@

```{r}
#| label: tbl-metrics
#| tbl-cap: Results of MAE, RMSE, and $R^2$ for training data, testing data, and all datasets for MLR model and RF model
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-cor
#| fig-cap: Correlation between each numerical variable in the house price dataset for Nanjing
#| echo: false
#| warning: false
#| message: false
